Cards model analysis

### 2020-11-18 cards_model_analysis.Rmd
README updates and as-yet-uncommited analyses

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval", "exact_eval/metaclass_lesion", "exact_eval/nonhomoiconic")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")

@@

```{r}
config_d = load_d(parent_dir, subdirs, num_runs, "run_config")
loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
lang_d = load_d(parent_dir, language_subdirs, num_runs, "language_losses")
meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
```

@@

@@

>>>>

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval", "exact_eval/metaclass_lesion", "exact_eval/nonhomoiconic")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")
language_meta_subdirs = c("exact_eval/language_meta", "exact_eval/language_meta_2", "exact_eval/language_meta_3", "exact_eval/language_meta_4")

@@

```{r}
config_d = load_d(parent_dir, subdirs, num_runs, "run_config")
loss_d = load_d(parent_dir, subdirs, num_runs, "losses")
lang_d = load_d(parent_dir, language_subdirs, num_runs, "language_losses")
meta_true_d = load_d(parent_dir, subdirs, num_runs, "meta_true_losses")
lang_meta_true_d = load_d(parent_dir, language_meta_subdirs, num_runs, "language_meta_true_losses")
```

@@

```{r}
lang_meta_true_d = lang_meta_true_d %>%
  filter(epoch %% 100 == 0) %>%
  gather(task, loss, -epoch, -run, -run_type) %>%
  separate(task, c("meta_task", "mapping_toe", "base_task_toe", "source", "target"), ":|->")

@@

# language meta

```{r}
ggplot(lang_meta_true_d %>% 
         filter(meta_task == "toggle_losers"),
       aes(x=epoch, y=loss, color=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ run)
```

```{r}
ggplot(lang_meta_true_d %>% 
         filter(meta_task == "toggle_losers",
                source == "game_straight_flush_l_0_bv_0_sr_0"),
       aes(x=epoch, y=loss, color=base_task_toe)) +
  geom_line(stat="summary",
            fun.y="mean") +
  facet_grid(run_type ~ run)
```
